% Acknowledgements

\pdfbookmark[1]{Acknowledgements}{Acknowledgements} % Bookmark name visible in a PDF viewer



\bigskip

%----------------------------------------------------------------------------------------

\begingroup

\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Acknowledgements}
The journey I started almost four years ago was for sure not an easy one and I would have not been able to complete this PhD thesis without the support of many people.

I want to thank both of my supervisors Daniel and Giulio for being great mentors, advisers and wonderful human beings. I am grateful for your encouragement, guidance, and advice throughout this whole process. Thank you for making sure that I gave the best of myself and constantly reminding me how ridiculous I can be at times!

I am indebted to my co-authors, as this thesis contains many of their thoughts and ideas. I would also like to thank past and present members of the Stouffer Lab Tylianakis Lab for inspiring for me to give the best of myself even when it was hard at times. Many thanks to current members of the DaRe group for always being supportive, especially over the past six months. 
A special thanks to Michelle---it’s been great sharing this journey with you. Thanks for your encouragement and always being available to listen to all of my crazy ideas! 

I would also like to thank the wonderful people that I met over the past years: Mareike, Rudolf, Michal, Alex in the School of Biological Sciences; Liz, Gerry, Sahana and DD in the School of Mathematics \& Statistics; the Zumba crew and the running club from the UC RecCentre; all the wonderful aerialists and polers from Altitude and Circortica. Thank you all for keeping up with my craziness---especially over the past couple of months.

Last but not least, I would like to thank my family, especially my amazing sister Owendini and her family for all their moral support. A special thanks to Alex and Emrick: thank you for all your words of encouragement and the laughs --- especially during the writing phase!
%\noindent Put your acknowledgements 
%here.\\



\endgroup